Gravitational Lens Recovery with \Glass: Measuring the mass profile and shape of a lens

### 2014-06-04 limits/ms.tex
More corrections.

The rather complicated dependence of lensing observables on the mass
distribution $\kappa(\vec\theta)$ has an important consequence: very different
mass distributions can result in similar observables.  This is the phenomenon
of lensing degeneracies.  While the non-uniqueness of lens models noted by
\cite{1981ApJ...244..736Y} already hinted at degeneracies, their existence was
first derived by \cite{1985ApJ...289L...1F}.  The most important is the
so-called mass-sheet degeneracy, which is that image positions remain invariant
if $\tau(\vec\theta)$ is multiplied by an arbitrary constant.  This corresponds
to rescaling the surface density at the images $\kappa(\vec\theta)$. In fact
there are infinitely many degeneracies \citep{2000AJ....120.1654S} because any
transformation of the arrival-time surface away from the images has no effect
on the lensing observables.  In particular, there are degeneracies that involve
the shape of the mass distribution
\citep{2006ApJ...653..936S,2013arXiv1306.4675S}.  Degeneracies tend to be
suppressed if there are sources at very different redshifts or `redshift
contrast' \citep{1998AJ....116.1541A,2009ApJ...690..154S}, because the presence
of different factors of $D_S/D_{LS}$ in the image plane makes it more difficult
to change the mass distribution and the arrival-time surface without affecting
the lensing observables.  But degeneracies are still present with multiple
source redshifts.  \citep{2008MNRAS.386..307L}.

>>>>

The rather complicated dependence of lensing observables on the mass
distribution $\kappa(\vec\theta)$ has an important consequence: very different
mass distributions can result in similar observables.  This is the phenomenon
of lensing degeneracies.  While the non-uniqueness of lens models noted by
\cite{1981ApJ...244..736Y} already hinted at degeneracies, their existence was
first derived by \cite{1985ApJ...289L...1F}.  The most important is the
so-called mass-sheet degeneracy, which is that image positions remain invariant
if $\tau(\vec\theta)$ is multiplied by an arbitrary constant.  
\hilight{This corresponds
to rescaling the surface density at the images $\kappa(\vec\theta)$.} In fact
there are infinitely many degeneracies \citep{2000AJ....120.1654S} because any
transformation of the arrival-time surface away from the images has no effect
on the lensing observables.  In particular, there are degeneracies that involve
the shape of the mass distribution
\citep{2006ApJ...653..936S,2013arXiv1306.4675S}.  Degeneracies tend to be
suppressed if there are sources at very different redshifts or `redshift
contrast' \citep{1998AJ....116.1541A,2009ApJ...690..154S}, because the presence
of different factors of $D_S/D_{LS}$ in the image plane makes it more difficult
to change the mass distribution and the arrival-time surface without affecting
the lensing observables.  But degeneracies are still present with multiple
source redshifts.  \citep{2008MNRAS.386..307L}.
